### 2021-04-28 paper/output/document/paper22.tex
prof amin's feedback
added kroy and prettified

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{2}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL Implementation%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Isabelle/HOL is an interactive proof assistant \cite{isabelle} built on Haskell and Scala. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

@@

\isamarkupcmt{t represents a set of DDL formulas.%

@@

\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set {``True"}

@@

\isamarkupcmt{set of propositions obligatory in this "context"%

@@

\isamarkupcmt{ob(context)(term) is True if t is obligatory in this context%

@@

as a HOL formula. A formula defined with the \isatt{abbreviation} command is unfolded in every 
instance. While the shallow embedding is generally performant (because it uses Isabelle's original 
syntax tree), abbreviations may possibly hurt performance. In some complicated proofs, we want controlled
unfolding. Benzmueller and Parent told me that eventually, the performance cost of abbreviations can 

@@

Nitpick successfully found a model satisfying these axioms so the system is consistent.\cite{hintikka}%

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
{\color{red} Nitpick} \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper22.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%56=22%:%
%:%68=24%:%
%:%70=26%:%
%:%71=26%:%
%:%72=26%:%
%:%73=26%:%
%:%74=27%:%
%:%75=28%:%
%:%76=28%:%
%:%77=28%:%
%:%78=28%:%
%:%80=29%:%
%:%81=30%:%
%:%82=30%:%
%:%85=44%:%
%:%87=46%:%
%:%88=46%:%
%:%89=46%:%
%:%90=46%:%
%:%91=47%:%
%:%92=47%:%
%:%93=47%:%
%:%101=51%:%
%:%113=53%:%
%:%114=54%:%
%:%115=55%:%
%:%116=56%:%
%:%118=80%:%
%:%119=81%:%
%:%120=82%:%
%:%122=83%:%
%:%123=84%:%
%:%124=85%:%
%:%125=86%:%
%:%126=86%:%
%:%134=93%:%
%:%146=95%:%
%:%147=96%:%
%:%148=97%:%
%:%149=98%:%
%:%150=99%:%
%:%151=100%:%
%:%155=116%:%
%:%157=117%:%
%:%158=117%:%
%:%159=118%:%
%:%160=119%:%
%:%161=119%:%
%:%162=120%:%
%:%164=122%:%
%:%166=123%:%
%:%167=123%:%
%:%168=124%:%
%:%170=125%:%
%:%171=125%:%
%:%174=145%:%
%:%175=146%:%
%:%177=147%:%
%:%178=147%:%
%:%179=148%:%
%:%180=149%:%
%:%181=149%:%
%:%182=150%:%
%:%184=151%:%
%:%187=153%:%
%:%189=154%:%
%:%190=154%:%
%:%191=155%:%
%:%199=162%:%
%:%211=164%:%
%:%212=165%:%
%:%213=166%:%
%:%214=167%:%
%:%215=168%:%
%:%219=170%:%
%:%221=171%:%
%:%222=171%:%
%:%223=171%:%
%:%225=171%:%
%:%229=171%:%
%:%230=171%:%
%:%232=172%:%
%:%233=173%:%
%:%234=173%:%
%:%236=174%:%
%:%237=175%:%
%:%238=176%:%
%:%248=178%:%
%:%249=179%:%
%:%250=180%:%
%:%251=181%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{2}}{\isadigit{2}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Isabelle/HOL Implementation \label{sec:isabelle}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Isabelle/HOL is an interactive proof assistant \cite{isabelle} built on Haskell and Scala. It 
allows the user to define types, functions, definitions, and axiom systems. It has built-in support for both
automatic and interactive/manual theorem proving.

@@

\isamarkupcmt{t represents a set of DDL formulae.%

@@

\isamarkupcmt{A set of formulae is defined by its truth value at a set of worlds. For example, the set \{True\}

@@

\isamarkupcmt{set of propositions obligatory in this context%

@@

\isamarkupcmt{ob(context)(term) is True if the term is obligatory in this context%

@@

as a HOL formula. Isabelle automatically unfolds formulae defined with the \isatt{abbreviation} command 
whenever they are applied. While the shallow embedding is performant (because it uses Isabelle's original 
syntax tree), abbreviations may hurt performance. In some complicated proofs, we want to control definition
unfolding. Benzmueller and Parent told me that the performance cost of abbreviations can 

@@

Nitpick successfully found a model satisfying these axioms so the system is consistent.%

@@

  Empty assignment \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Nitpick \cite{nitpick} can generate models or countermodels, so it's useful to falsify potential
theorems, as well as to show consistency. {\color{red} by simp} indicates the proof method. In this 
case, {\color{red} simp} indicates the Simplification proof method, which involves unfolding definitions
and applying theorems directly. HOL has $True$ as a theorem, which is why this theorem was so easy to prove.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper22.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%47=19%:%
%:%56=22%:%
%:%68=24%:%
%:%70=26%:%
%:%71=26%:%
%:%72=26%:%
%:%73=26%:%
%:%74=27%:%
%:%75=28%:%
%:%76=28%:%
%:%77=28%:%
%:%78=28%:%
%:%80=29%:%
%:%81=30%:%
%:%82=30%:%
%:%85=44%:%
%:%87=46%:%
%:%88=46%:%
%:%89=46%:%
%:%90=46%:%
%:%91=47%:%
%:%92=47%:%
%:%93=47%:%
%:%101=51%:%
%:%113=53%:%
%:%114=54%:%
%:%115=55%:%
%:%116=56%:%
%:%118=80%:%
%:%119=81%:%
%:%120=82%:%
%:%122=83%:%
%:%123=84%:%
%:%124=85%:%
%:%125=86%:%
%:%126=86%:%
%:%134=93%:%
%:%146=95%:%
%:%147=96%:%
%:%148=97%:%
%:%149=98%:%
%:%150=99%:%
%:%151=100%:%
%:%155=116%:%
%:%157=117%:%
%:%158=117%:%
%:%159=118%:%
%:%160=119%:%
%:%161=119%:%
%:%162=120%:%
%:%164=122%:%
%:%166=123%:%
%:%167=123%:%
%:%168=124%:%
%:%170=125%:%
%:%171=125%:%
%:%174=145%:%
%:%175=146%:%
%:%177=147%:%
%:%178=147%:%
%:%179=148%:%
%:%180=149%:%
%:%181=149%:%
%:%182=150%:%
%:%184=151%:%
%:%187=153%:%
%:%189=154%:%
%:%190=154%:%
%:%191=155%:%
%:%199=162%:%
%:%211=164%:%
%:%212=165%:%
%:%213=166%:%
%:%214=167%:%
%:%215=168%:%
%:%219=170%:%
%:%221=171%:%
%:%222=171%:%
%:%223=171%:%
%:%225=171%:%
%:%229=171%:%
%:%230=171%:%
%:%232=172%:%
%:%233=173%:%
%:%234=173%:%
%:%236=174%:%
%:%237=175%:%
%:%238=176%:%
%:%248=178%:%
%:%249=179%:%
%:%250=180%:%
%:%251=181%:%
